Assessing primitives performance\\ on multi-stage execution

### 2018-05-09 paper.tex
add extra collumn to the asm comparison table

Our evaluation is based on the Cog VM a Smalltalk virtual machine. The Cog VM is based on Dan Ingalls' Smalltalk VM \cite{BackToTheFuture} and \sd{has} have been enhanced with a JIT \cite{CogJIT} compiling one method or closure at a time to native code. Historically, the VM implemented a 32-bits adaptation of the Smalltalk-80 specifications \cite{blueBook}, but the Cog VM is now the default VM for multiple programming languages such as Pharo \cite{PharoByExample}, Squeak \cite{SqueakByExample} and Newspeak \cite{NewspeakOopsla}.

>>>>

Our evaluation is based on the Cog VM a Smalltalk virtual machine. The Cog VM is based on Dan Ingalls' Smalltalk VM \cite{BackToTheFuture} and has been enhanced with a JIT \cite{CogJIT} compiling one method or closure at a time to native code. Historically, the VM implemented a 32-bits adaptation of the Smalltalk-80 specifications \cite{blueBook}, but the Cog VM is now the default VM for multiple programming languages such as Pharo \cite{PharoByExample}, Squeak \cite{SqueakByExample} and Newspeak \cite{NewspeakOopsla}.
